Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-23 doc/bcspaper/article.tex
Removed some of the strikethrough bits since they were breaking pdflatex for me and we were going to omit them anyway (easy to get them back using VCS)

\section{Introduction} \label{sec:1} Since the advent of the `Digital Age' and
the ability of computers to copy and reproduce information for a negligible
cost, the amount of information available to researchers has been increasing
drastically. \st{ B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million
papers were published in the year 2006 alone\cite{bjork2009}}. As available
information increases, relevant material becomes progressively more difficult
to find manually and the need for an automated information retrieval tool more
apparent.  There are already a large number of information retrieval and
recommendation systems for scientific publications.  Many of these systems,
such as AGRICOLA (\url{http://agricola.nal.usda.gov/}), the Cochrane
Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
(\url{http://www.textpresso.org/}) index only publications from predefined
journals or topics (for the above examples, Agriculture, Biology and
Bioinformatics respectively).  Unfortunately, these domain specific indexing
systems usually only contain a small subset of papers, excluding potentially
crucial literature because it does not quite fit into the subject domain. 
%This problem is often exacerbated by the decision to leave out some papers and
%articles because the system administrators do not have permission from the
%author or publisher to include them. 
The value of these systems to their users is often restricted by the small
proportion of available literature that they index, forcing researchers to use
multiple, domain specific, search engines for their queries.  In contrast,
there are also a number of interdisciplinary indexing systems and online
journals such as arXiv( \url{http://arxiv.org/}),
PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}),
that try to incorporate wide ranges of papers from as many disciplines as
possible. The traits of these systems often complement those of their
domain-specific counterparts; they provide a comprehensive collection of
literature but insufficient filtering and indexing capabilities.  One of the
most publicised and well known interdisciplinery scientific literature search
systems is Google Scholar (\url{http://scholar.google.com}). Google offers
advanced query options specific to Scholar that allow searching by author, year
and for words that occur only in the document title.

@@

%Use the template \emph{chapter.tex} together with the Springer document class SVMono (monograph-type books) or SVMult (edited books) to style the various elements of your chapter content in the Springer layout.

%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations. And please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

@@

\subsection*{Collection of scientific articles}
Partridge allows users to upload any paper which is free of copyright restrictions.
For the purpose of this study we needed a large set of papers that we could label with CoreSC
to investigate how this information assists classification into paper type.
Open Access (OA) journals \st{are research journals that provide their papers free
to read online, often making revenue by charging authors to publish their
articles \cite{solomon2012study}.  Many OA journals} provide free read access to
their papers, but do not permit the user of articles for data mining purposes.
The PLoS journals\footnote{PLoS: \url{http://www.plos.org/}} contain large
volumes of OA literature under a permissive license that allows data mining.
They also use the Pubmed Central markup schema, which is compatible with SAPIENTA,
for papers published through their journal.  The PLoS journals advanced search
offers approximately 50 types of paper through which to restrict the search.
Many of these paper type categories contain too few papers to be useful, others
are too specific (e.g.``Message from PLoS'') or appear rather adhoc. 
Indeed it is not clear how these paper types have been identified. % in conclusions add how this can give recommendations for Plos and other journals
We chose to look at a range of types, some of which
we expect to overlap or have an unclear distinction.
These are namely: Essay, Correspondence, Case Study, Synopsis, Perspective, Viewpoint, Opinion,
Review, Research). 
%how papers were acquired 
The papers were downloaded from PLoS using {\em plosget.py}, a short python
script that uses the PLoS restful search API. The number of papers downloaded
per paper type category was as follows: 200 Essay, 99 Correspondence, 174
Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 107 Case Study, 312
Review, 200 Research.  These formed a corpus of 1459 papers.

>>>>

\section{Introduction} \label{sec:1} Since the advent of the `Digital Age' and
the ability of computers to copy and reproduce information for a negligible
cost, the amount of information available to researchers has been increasing
drastically. As available information increases, relevant material becomes
progressively more difficult to find manually and the need for an automated
information retrieval tool more apparent.  There are already a large number of
information retrieval and recommendation systems for scientific publications.
Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}),
the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
(\url{http://www.textpresso.org/}) index only publications from predefined
journals or topics (for the above examples, Agriculture, Biology and
Bioinformatics respectively).  Unfortunately, these domain specific indexing
systems usually only contain a small subset of papers, excluding potentially
crucial literature because it does not quite fit into the subject domain.

The value of these systems to their users is often restricted by the small
proportion of available literature that they index, forcing researchers to use
multiple, domain specific, search engines for their queries.  In contrast,
there are also a number of interdisciplinary indexing systems and online
journals such as arXiv( \url{http://arxiv.org/}),
PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}),
that try to incorporate wide ranges of papers from as many disciplines as
possible. The traits of these systems often complement those of their
domain-specific counterparts; they provide a comprehensive collection of
literature but insufficient filtering and indexing capabilities.  One of the
most publicised and well known interdisciplinery scientific literature search
systems is Google Scholar (\url{http://scholar.google.com}). Google offers
advanced query options specific to Scholar that allow searching by author, year
and for words that occur only in the document title.

@@

@@

\subsection*{Collection of scientific articles} Partridge allows users to
upload any paper which is free of copyright restrictions.  For the purpose of
this study we needed a large set of papers that we could label with CoreSC to
investigate how this information assists classification into paper type.  Open
Access (OA) journals provide free read access to their papers, but many do not
permit the user of articles for data mining purposes.  The PLoS
journals\footnote{PLoS: \url{http://www.plos.org/}} contain large volumes of OA
literature under a permissive license that allows data mining.  They also use
the Pubmed Central markup schema, which is compatible with SAPIENTA, for papers
published through their journal.  The PLoS journals advanced search offers
approximately 50 types of paper through which to restrict the search.  Many of
these paper type categories contain too few papers to be useful, others are too
specific (e.g.``Message from PLoS'') or appear rather adhoc.  Indeed it is not
clear how these paper types have been identified. % in conclusions add how this
can give recommendations for Plos and other journals We chose to look at a
range of types, some of which we expect to overlap or have an unclear
distinction.  These are namely: Essay, Correspondence, Case Study, Synopsis,
Perspective, Viewpoint, Opinion, Review, Research).

The papers were downloaded from PLoS using {\em plosget.py}, a short python
script that uses the PLoS restful search API. The number of papers downloaded
per paper type category was as follows: 200 Essay, 99 Correspondence, 174
Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 107 Case Study, 312
Review, 200 Research.  These formed a corpus of 1459 papers.
